%% \chapter[htoc-titlei][hhead-titlei]{htitlei}
%% -----------------------------------------------------------------------------
\chapter[The Large Hadron Collider][The Large Hadron Collider]{The Large Hadron Collider}
\section{The Large Hadron Collider}

The Large Hadron Collider(LHC) is the world's highest energy particle accellerator 
and is located 100m underneath the Franco-Swiss border at the European Organization
for Nuclear Research (CERN) in a 26.7 km tunnel. 

The LHC is a ciruclar 
machine capable of accelerating beams of protons and colliding them at center of mass 
energies up to $\sqrt{s} = 14 TeV$ at 4 collision sites around the ring, where 4 experiments
are housed (ATLAS, CMS, LHCb, and ALICE). The LHC also operates in a modes with beams of 
heavy ions. The LHC is composed of thousands of super-conducting Niobium-Titantium 
magnets, cooled to 2.7$^\circ$ degrees
% magnets


The technology involved in the development of the LHC is an enormous achievement
it its own right and is documented in detail here. 

\subsection{The Accelerator Complex}

The accelerator complex is a progressive series of machineswith the LHC as the final stage.
Protons are obtained from hydrogen atoms and are accelerated to 50 MeV using the
Linac2, before being injected into the Proton-Synchrotron Booster (PSB). In
the PSB the protons are accelerated to energies of 1.4 GeV for injection
in to the Proton-Synchrotron (PS). The PS accelerates the protons to 25 GeV
and dumps bunches into the Super Proton Synchrotron (SPS), where they 
are accelerated to 450 GeV and finally dumped into the LHC. 

\subsection{Beam Parameters and Collisions} 




\section{The 2012 Dataset} 
